4-examples

### 2022-06-15 4-1-basic.Rmd

## Victoria COVID data {#covid}

The Victoria State Government in Australia provides daily COVID information about the source and local government area (LGA) of recorded cases. This data can be used to visualise COVID spread when combined with map information available from the Australian Bureau of Statistics. Here we will use the data to demonstrate how to match sites between these two tables with \pkg{cubble} in the case of a few mismatches. The first five rows the data are printed below:

@@

```{r echo = TRUE}
covid |> head(5)
lga |> head(5)
```

A \code{cubble} object can be created from separate spatial and temporal tables in a list, the other arguments (\code{key}, \code{index}, and \code{coords}) are described in Section \@ref(create). The function \code{as_cubble()} will automatically try to match the sites in both tables and show a warning message in case of missing information (mismatch between the sites in the two tables).

>>>>

## Victoria COVID spatio-temporal incidence and spread {#covid}

Since the start of the pandemic, the Victoria State Government in Australia has provided daily COVID counts by local government area (LGA). This data can be used to visualise COVID incidence and spread spatially, when combined with map polygon data available from the Australian Bureau of Statistics. These different sources need to be combined for the analysis, by matching the LGA names. Here is how to do this with \pkg{cubble}, including how to handle mismatches arising from different names of the same LGAs in the two tables. The COVID data is a `csv` and looks like:

@@

```{r}
covid |> head(5)
```

and the spatial polygons are an ESRI shapefile that looks like:

```{r}
lga |> head(5)
```

The function \code{as_cubble()} is used to create a \code{cubble} object from the two spatial and temporal tables, and requires specifying the arguments (\code{key}, \code{index}, and \code{coords}) (as described in Section \@ref(create)). It will automatically try to match the sites in both tables and will show a warning message when there are mismatches, as shown below:
